\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[ruled,vlined]{algorithm2e}
\DeclareUnicodeCharacter{2212}{-}


\newcommand{\newpar}{\vspace{.2in} \noindent}
\usepackage[margin=1.2in]{geometry}

\title{COMP3821 Homework 4}
\author{Jason Qin, z5258237}
\date{April 2020}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle

\section*{Question 2.}
\paragraph{2.1} \textbf{Variables.} \\

\noindent
\begin{enumerate}
    \item $n$ is the number of distinct toy $i$'s that can be produced. \\
    \item $m$ is the number of factories $f_j$ availiable for producing toys. \\
    \item $C_i$ is the setup cost for a toy $i$. \\
    \item $P_i$ is the profit for selling each toy $i$. \\
    \item $H_j$ is the total production hours for factory $j$, $h_j$ is the hours used. \\
    \item $A_{ij}$ is the production rate (toys/hour) of toy $i$ at factory $j$. \\
    \item $S$ is the resulting map of factories to tuples containing the number of toys e.g. (toy $1$: 4, toy $2$: 5). \\
    \item $k_i$ is the number of toys $i$'s made at a factory.
\end{enumerate}

\paragraph*{2.2} \textbf{Constraints.} \\

\noindent
\begin{enumerate}
    \item $(\sum_{i=1}^{n}k_i \times P_i - C_i) \geq 0$ to make a net profit at factory $j$. If a factory is not being used, i.e. it is not worth it to make toys there, then its profit margin is simply $0$.\\
    \item $h_j \leq H_j$ for all $0 \leq j \leq m$.
\end{enumerate}

\paragraph*{2.3} \textbf{Objective.} \\

\noindent
Maximize the net profits per factory to obtain the maximum total profit from selling toys.
Hence the goal is to maximize,

$$\sum_{s_j \in S}^{m} profit(s_j)$$

where profit() sums up
the net profit of made at a factory $j$.

\paragraph*{2.4} \textbf{Polynomial-Time Solution.} \\

\noindent
Since this is an integer LP problem, it is fundamentally NP-hard with no deterministic polynomial-time solution.
However, a polynomial solution may exist for specific instances of the integer LP problem. This could be one, although, it is not known.


\end{document}
